%-------------------------
% Resume in Latex
% Author : Jose Antonio Chaires Monroy
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Jose Antonio Chaires Monroy} \\ \vspace{1pt}
    \href{mailto:antonioch.mon@gmail.com}{\underline{antonioch.mon@gmail.com}} $|$
    \href{https://linkedin.com/in/antonioch-mon}{\underline{linkedin.com/in/antonioch-mon}} $|$
    \href{https://github.com/antonieto}{\underline{github.com/antonieto}}
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
      {Production Engineer}{October 2024 --- Present}
	  {Meta - AI Training (RecSys) Infrastructure}{New York, NY}
      \resumeItemListStart
	    
        \resumeItem{Fixed a \textbf{performance regression} in the job ranker's \textbf{critical logging path} that caused \textbf{30+ min SLI data lag} — leaving the team blind to incidents — and triggered \textbf{MySQL connection exhaustion} and \textbf{data loss} across ranking iterations; reduced lag to \textbf{under 200s}.}
        \resumeItem{Scaled a \textbf{ML training log stream processing system's} infrastructure to \textbf{210 hosts}, reducing log latency from \textbf{10 hours to 3 minutes}.}
        \resumeItem{Built a \textbf{fleetwide Python profiling pipeline} to surface GPU efficiency insights across ML training jobs, producing a \textbf{technical finding} that \textbf{4\%} of GPU startup time is lost to imports — providing actionable \textbf{technical direction} for codebase hygiene at scale.}
        \resumeItem{Drove \textbf{AI adoption} by building an \textbf{agentic workflow} that automated \textbf{integration test authoring}, producing a \textbf{10k-line test suite} that caught \textbf{2 critical incidents}.}
      \resumeItemListEnd

  \resumeSubheading
      {Full Stack Software Engineer}{February 2024 --- August 2024}
      {Atrato (YC 21)}{Guadalajara, MX (Remote)}
      \resumeItemListStart
        \resumeItem{Resolved a \textbf{QPS-induced service reliability} issue on a business-critical endpoint by implementing a \textbf{load-shedding queue}, which also unlocked \textbf{bulk transaction ingestion} for finance agents — saving \textbf{10 hrs/week} in manual operations.}
        \resumeItem{Delivered \textit{Multicredito} — a \textbf{multi-loan BNPL} feature deferred for years due to complexity — by designing and building the \textbf{API} and \textbf{UI}, enabling users to hold and manage multiple loans simultaneously at independent terms.}
        \resumeItem{Migrated a \textbf{MySQL-backed in-house logger} — whose table had grown unqueryable — to \textbf{AWS CloudWatch} with a \textbf{codebase-wide refactor} completed in \textbf{2 weeks}.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineering Intern}{June 2023 --- September 2023}
      {Google - Core Machine Learning Foundation}{Sunnyvale, CA}
      \resumeItemListStart
        \resumeItem{Built a \textbf{benchmarking} application for software and ML engineers to identify \textbf{performance regressions} across internal and open-source \textbf{ML models}.}
        \resumeItem{Built a \textbf{Python job queue} and \textbf{UI} for capacity-constrained \textbf{ML performance test} scheduling, replacing a brittle \textbf{manual CLI} that failed under load with a \textbf{self-service} workflow.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{January 2023 -- June 2023}
      {Lizza (YC W22)}{Guadalajara, MX}
      \resumeItemListStart
        \resumeItem{Rewrote a database migration pipeline in \textbf{Go} with a \textbf{maximally parallelizable} architecture, cutting runtime from \textbf{20+ hours to under 5 minutes} (\textbf{288x speedup}) and unblocking the full deployment of a new backend.}
    \resumeItemListEnd

    \resumeSubheading
      {STEP Intern}{June 2022 -- September 2022}
      {Google - Core Finance Works}{Manhattan (remote), NY}
    \resumeItemListStart
        \resumeItem{Built a client-side \textbf{HTTP cache layer} for an internal \textbf{Angular/TypeScript} app, \textbf{achieving 40\% hit ratio} and improving responsiveness.}
        \resumeItem{Designed an internal \textbf{framework API extension} that improved customizability of auto-generated dropdowns.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Developer}{January 2022 -- June 2022}
      {Atrevi}{Guadalajara, MX}
      \resumeItemListStart
        \resumeItem{Assumed a \textbf{technical leadership} role in a small team building a \textbf{personal finance coach} mobile app.}
        \resumeItem{Architected the \textbf{state management} layer for the \textbf{React Native} frontend and led the design of the app's \textbf{authentication} backbone, backed by \textbf{AWS} and a \textbf{Django} REST API.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {Tecnologico de Monterrey $|$ \textbf{GPA 98.17/100 (4.0/4.0)}}{Guadalajara, Mexico.}
      {B.S Computer Science and Technology}{August 2020 -- June 2024}
  \resumeSubHeadingListEnd


% %-----------PROJECTS-----------
% \section{Projects}
%     \resumeSubHeadingListStart
%       \resumeProjectHeading
%           {\textbf{IJALTI Recruitment Tool} $|$ \emph{Typescript, Google Cloud Platform, PostgreSQL}}{March 2022 -- June 2022}
%           \resumeItemListStart
%             \resumeItem{Software Development course final project. Recruiting tool for mexican IT association.}
%             \resumeItem{Designed and developed a \textbf{NodeJS} monolithic application with the backend team, building several services using \textbf{ExpressJS}, \textbf{TypeScript} and \textbf{PostgreSQL}, integration Google Cloud Platform authentication services.}
%             \resumeItem{Built and integrated a \textbf{search mechanism} for a React application, designing and developing several UI components.}
%           \resumeItemListEnd
%     \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, TypeScript, Go, Python, C++, SQL (Postgres, MySQL), Rust, MATLAB.} \\
     \textbf{Frameworks}{: React, Angular, Next.js, Django, Spring Boot, Flask, Fast API.} \\
     \textbf{Developer Tools}{: Claude Code, Git, Neovim, Linux, Docker, Kubernetes, GitHub Actions, Bash scripting.} \\
     \textbf{Libraries}{: Tensorflow, Matplotlib, NumPy, gRPC, PyTorch}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}

